---
title: "Cleaning & Feature Engineering"
author: "Sahitya"
date: "29/04/2020"
output: html_document
---


```{r}
library(caret)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(tidyr)
#library(rapportools)
```

Loading the train data

```{r}
# Load train data - Replace blank cells with NA
df_x_main <- read.csv('airbnb_train_x.csv', na.strings = c("", "NA"))
df_y <- read.csv('airbnb_train_y.csv', na.strings = c("", "NA"))
df_x <- df_x_main
```

Loading the test data

```{r}
tdf_x_main <- read.csv('airbnb_test_x.csv', na.strings = c("", "NA"))
tdf <- tdf_x_main
```


Check for missingness

```{r}
# Check for missingness
colSums(is.na(df_x))
```

There are a lot of columns with missing data but it's easier to understand using proportions

```{r, fig.width=10,fig.height=10}

# missing.values <- df_x_main %>%
#   gather(key = "key", value = "val") %>%
#   mutate(isna = is.na(val)) %>%
#   group_by(key) %>%
#   mutate(total = n()) %>%
#   group_by(key, total, isna) %>%
#   summarise(num.isna = n()) %>%
#   mutate(pct = num.isna / total * 100)
# 
# 
# levels <-
#     (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key
# 
# percentage.plot <- missing.values %>%
#       ggplot() +
#         geom_bar(aes(x = reorder(key, desc(pct)),
#                      y = pct, fill=isna),
#                  stat = 'identity', alpha=0.8) +
#       scale_x_discrete(limits = levels) +
#       scale_fill_manual(name = "",
#                         values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
#       coord_flip() +
#       labs(title = "Percentage of missing values", x =
#              'Variable', y = "% of missing values")
# 
# percentage.plot

```

We can also see how the rows are -

```{r, fig.width=10,fig.height=10}
# row.plot <- df_x %>%
#   mutate(id = row_number()) %>%
#   gather(-id, key = "key", value = "val") %>%
#   mutate(isna = is.na(val)) %>%
#   ggplot(aes(key, id, fill = isna)) +
#     geom_raster(alpha=0.8) +
#     scale_fill_manual(name = "",
#         values = c('steelblue', 'tomato3'),
#         labels = c("Present", "Missing")) +
#     scale_x_discrete(limits = levels) +
#     labs(x = "Variable",
#            y = "Row Number", title = "Missing values in rows") +
#     coord_flip()
# 
# row.plot
```

In dealing with the missingness, let's first create missingness indicators for all the variables. For this, we can define a function. We shall use this once we are sure we've made a fair amount of cleaning to most of the columns.

```{r}
appendNAs <- function(dataset, cols) {
  append_these = data.frame( is.na(dataset[, cols] ))
  names(append_these) = paste(names(append_these), "NA", sep = "_")
  dataset = cbind(dataset, append_these)
  dataset[is.na(dataset)] = -1
  return(dataset)
}
```

A glimpse at the structure of the data

```{r}
glimpse(df_x)
```

Inspect the columns that have numeric data -

1	accommodates	Factor
2	availability_30	Factor
3	availability_365	int
4	availability_60	Factor
5	availability_90	Factor
6	bathrooms	Factor
7	bedrooms	Factor
8	beds	Factor
9	cleaning_fee	Factor - (needs to be cleaned - has $ symbol like $250.00)
10	extra_people	Factor - (needs to be cleaned - has $ symbol like $250.00)
11	guests_included	num
12	host_acceptance_rate	Factor - (needs to be cleaned - has format like so - 100%)
13	host_listings_count	Factor
14	host_response_rate	Factor - (needs to be cleaned - has format like so - 100%)
15	host_total_listings_count	Factor
16	latitude	Factor
17	longitude	Factor
18	maximum_nights	num
19	minimum_nights	int
20	monthly_price	Factor - (needs to be cleaned - has $ symbol like $250.00)
21	price	Factor - (needs to be cleaned - has $ symbol like $250.00)
22	security_deposit	Factor - (needs to be cleaned - has $ symbol like $250.00)
23	square_feet	int 
24	weekly_price	Factor - (needs to be cleaned - has $ symbol like $250.00)

First let's explore the columns with the $ symbols and commas and percentages -

```{r, fig.width=10,fig.height=150}

dollar_num_cols = c("cleaning_fee", "extra_people", "monthly_price", "price", "security_deposit", "weekly_price")
perc_num_cols = c("host_acceptance_rate", "host_response_rate")

# The columns which have prices
qplot(cleaning_fee, data = df_x) + coord_flip()
qplot(extra_people, data = df_x) + coord_flip()
qplot(monthly_price, data = df_x) + coord_flip()
qplot(price, data = df_x) + coord_flip()
qplot(security_deposit, data = df_x) + coord_flip()
qplot(weekly_price, data = df_x) + coord_flip()

# Observations

# cleaning_fee
# - Majority of NAs
# - Has a few f and t

# extra_people
# - has some longitude/latitude information -
# - 40.7115296729, 37.7172817854, 34.0550373047, 34.0544381605, 34.04703657, 34.0305066944, 33.9847962097, 33.7751358179, 30.3646152573

# price
# -looks fine except for a very small number of NAs

# security_deposit
# mostly NAs
# second most popular category is $0.00

# weekly_price
# - looks fine
# - mostly NAs

# monthly_price
# - NA is the most popular - there are lots
# - other values are mostly 4 digits or more with very few 3 digits

# The columns which have %
qplot(host_acceptance_rate, data = df_x) + coord_flip()
qplot(host_response_rate, data = df_x) + coord_flip()

# host_acceptance_rate
# - most popular category - NA
# - all others are within format

# host_response_rate
# - 100% is most popular
# - Next is NA
# - There are 4 out of place categories - Apartment, Loft, House, Condominium

```

Storing the discrepancies in a variable for later use -

```{r}
extra_people_discrepancies = c(40.7115296729, 37.7172817854, 34.0550373047, 34.0544381605, 34.04703657, 34.0305066944, 33.9847962097, 33.7751358179, 30.3646152573)
hostresponserate_discrepancies = c("Apartment", "Loft", "House", "Condominium")
```

```{r}
df_x[df_x$extra_people %in% extra_people_discrepancies,]
```

All the columns seem to be misplaced. We can store this separately and rearrange them -

```{r}
misplacedX <- c(16246, 30584, 47615, 56281, 65792, 72540, 75208, 92585, 96068)

misplaced_df_x <- df_x[df_x$extra_people %in% extra_people_discrepancies,]
df_x[df_x$extra_people %in% extra_people_discrepancies, 3:70] <- NA
df_x[df_x$X %in% misplacedX, ]
```

Now we can work on transforming the data -

```{r}
# First, the columns which have prices -

# cleaning_fee, extra_people, price, security_deposit, weekly_price, monthly_price

df_x$cleaning_fee <- as.numeric(str_replace_all(df_x$cleaning_fee, "[\\$,]", ""))
  # test data
tdf$cleaning_fee <- as.numeric(str_replace_all(tdf$cleaning_fee, "[\\$,]", ""))

df_x$extra_people <- as.numeric(str_replace_all(df_x$extra_people, "[\\$,]", ""))
  # test data
tdf$extra_people <- as.numeric(str_replace_all(tdf$extra_people, "[\\$,]", ""))

df_x$price <- as.numeric(str_replace_all(df_x$price, "[\\$,]", ""))
  # test data
tdf$price <- as.numeric(str_replace_all(tdf$price, "[\\$,]", ""))

df_x$security_deposit <- as.numeric(str_replace_all(df_x$security_deposit, "[\\$,]", ""))
  # test data
tdf$security_deposit <- as.numeric(str_replace_all(tdf$security_deposit, "[\\$,]", ""))

df_x$weekly_price <- as.numeric(str_replace_all(df_x$weekly_price, "[\\$,]", ""))
  # test data
tdf$weekly_price <- as.numeric(str_replace_all(tdf$weekly_price, "[\\$,]", ""))

df_x$monthly_price <- as.numeric(str_replace_all(df_x$monthly_price, "[\\$,]", ""))
  # test data
tdf$monthly_price <- as.numeric(str_replace_all(tdf$monthly_price, "[\\$,]", ""))

# Next, the columns which havedf_x$host_acceptance_rate - has %

# host_acceptance_rate, host_response_rate

df_x$host_acceptance_rate <- as.numeric(str_replace_all(df_x$host_acceptance_rate, "%", ""))
  # test data
tdf$host_acceptance_rate <- as.numeric(str_replace_all(tdf$host_acceptance_rate, "%", ""))

df_x$host_response_rate <- as.numeric(str_replace_all(df_x$host_response_rate, "%", ""))
  # test data
tdf$host_response_rate <- as.numeric(str_replace_all(tdf$host_response_rate, "%", ""))

```

The other columns now -

1	accommodates	Factor
2	availability_30	Factor
3	availability_365	int
4	availability_60	Factor
5	availability_90	Factor
6	bathrooms	Factor
7	bedrooms	Factor
8	beds	Factor
#  9	cleaning_fee	Factor - (needs to be cleaned - has $ symbol like $250.00)
#  10	extra_people	Factor - (needs to be cleaned - has $ symbol like $250.00)
11	guests_included	num
#  12	host_acceptance_rate	Factor - (needs to be cleaned - has format like so - 100%)
13	host_listings_count	Factor
#  14	host_response_rate	Factor - (needs to be cleaned - has format like so - 100%)
15	host_total_listings_count	Factor
16	latitude	Factor
17	longitude	Factor
18	maximum_nights	num
19	minimum_nights	int
#  20	monthly_price	Factor - (needs to be cleaned - has $ symbol like $250.00)
#  21	price	Factor - (needs to be cleaned - has $ symbol like $250.00)
#  22	security_deposit	Factor - (needs to be cleaned - has $ symbol like $250.00)
23	square_feet	int 
#  24	weekly_price	Factor - (needs to be cleaned - has $ symbol like $250.00)

```{r}
qplot(as.numeric(accommodates), data = df_x)
qplot(as.numeric(availability_30), data = df_x)
qplot(as.numeric(availability_365), data = df_x)
qplot(as.numeric(availability_60), data = df_x) + coord_flip()
qplot(as.numeric(availability_90), data = df_x) + coord_flip()
qplot(as.numeric(bathrooms), data = df_x) + coord_flip()
qplot(as.numeric(bedrooms), data = df_x)
qplot(as.numeric(beds), data = df_x)
qplot(as.numeric(guests_included), data = df_x) + coord_flip()
qplot(as.numeric(host_listings_count), data = df_x) + coord_flip()
qplot(as.numeric(host_total_listings_count), data = df_x) + coord_flip()
# qplot(longitude, data = df_x)
# qplot(latitude, data = df_x)
qplot(as.numeric(maximum_nights), data = df_x)
qplot(as.numeric(minimum_nights), data = df_x)
qplot(as.numeric(square_feet), data = df_x)
```

Visualize in log scale -

```{r}

qplot(as.numeric(accommodates), data = df_x) + scale_x_log10()
qplot(as.numeric(availability_30), data = df_x) + scale_x_log10()
qplot(as.numeric(availability_365), data = df_x) + scale_x_log10()
qplot(as.numeric(availability_60), data = df_x) + coord_flip() + scale_x_log10()
qplot(as.numeric(availability_90), data = df_x) + coord_flip() + scale_x_log10()
qplot(as.numeric(bathrooms), data = df_x) + coord_flip() + scale_x_log10()
qplot(as.numeric(bedrooms), data = df_x) + scale_x_log10()
qplot(as.numeric(beds), data = df_x) + scale_x_log10()
qplot(as.numeric(guests_included), data = df_x) + coord_flip() + scale_x_log10()
qplot(as.numeric(host_listings_count), data = df_x) + coord_flip() + scale_x_log10()
qplot(as.numeric(host_total_listings_count), data = df_x) + coord_flip() + scale_x_log10()
# qplot(longitude, data = df_x)
# qplot(latitude, data = df_x)
qplot(as.numeric(maximum_nights), data = df_x) + scale_x_log10()
qplot(as.numeric(minimum_nights), data = df_x) + scale_x_log10()
qplot(as.numeric(square_feet), data = df_x) + scale_x_log10()


```

Convert these columns to numeric

```{r}

num_cols <- c("accommodates", "availability_30", "availability_365", "availability_60", 
              "availability_90", "bathrooms", "bedrooms", "beds", "guests_included", 
              "host_listings_count", "host_total_listings_count", 
              "maximum_nights", "minimum_nights", "square_feet")

geo_cols <- c("latitude", "longitude")

df_x[,num_cols] <- sapply(df_x[,num_cols],as.numeric)
  # test data
tdf[,num_cols] <- sapply(tdf[,num_cols],as.numeric)

df_x[,geo_cols] <- sapply(df_x[,geo_cols],as.character)
df_x[,geo_cols] <- sapply(df_x[,geo_cols],as.numeric)
  # test data
tdf[,geo_cols] <- sapply(tdf[,geo_cols],as.character)
tdf[,geo_cols] <- sapply(tdf[,geo_cols],as.numeric)

```

Observations for these variables -


1. availability_30
- Mostly 0s
- There is f and t but negligible

2. availability_365
- Looks good
- Can be visualized in a log scale 

3. availability_60
- Unclear
- Need to look at the table
- Few values which are like so - "Santa Monica, California, United States" - Might have to find the rows where the data is shuffled like this

4. availability_90
- Unclear
- Need to look at the table
- Few values which are names I guess, like 'Amanda', 'Winni'

5. Bathrooms
- Mostly 1
- Has some names like 'Oceanview', 'North Shoal Creek', 'Long Beach'

6. Bedrooms 
- Decent - mostly 1
- has some values like - 'within an hour'

7. guests_included
- There is a negative scale in the graph - need to find out what this is about
- Otherwise, mostly 0

8. accommodates
- All good except for one t

9. host_listings_count
- Have to see in a table

10. maximum_nights
- Have to see in a table

11. minimum_nights 
- Have to see in a table

12. latitude, longitude
- Have to see in a table


```{r, fig.height=10, fig.width=30}
ggplot(gather(df_x[, num_cols]), aes(value)) + 
    geom_histogram(stat = "count") + 
    facet_wrap(~key, scales = 'free_x')
```

Now a look at categorical variables -

# 1	bed_type	Factor
# 2	cancellation_policy	Factor
# 3	city	Factor
# 4	city_name	Factor
# 5	country	Factor
# 6	country_code	Factor
# 7	experiences_offered	Factor
8	host_has_profile_pic	Factor
9	host_identity_verified	Factor
10	host_is_superhost	Factor
# 11	host_location	Factor
# 12	host_neighbourhood	Factor
# 13	host_response_time	Factor
14	instant_bookable	Factor
15	is_business_travel_ready	Factor
16	is_location_exact	Factor
# 17	jurisdiction_names	Factor
# 18	license	Factor
# 19	market	Factor
# 20	neighbourhood	Factor
# 21	property_type	Factor
22	require_guest_phone_verification	Factor
23	require_guest_profile_picture	Factor
24	requires_license	Factor
# 25	room_type	Factor
# 26	smart_location	Factor
# 27	state	Factor

There are a bunch of columns which have 't' and 'f'

1. df$host_has_profile_pic - factor
2. df$host_identity_verified - factor
3. df$host_is_superhost - factor
4. df$instant_bookable - factor
5. df$is_business_travel_ready - factor
6. df$is_location_exact - factor
7. df$require_guest_phone_verification - factor
8. df$require_guest_profile_picture - factor
9. df$requires_license - factor

First, histograms.

```{r echo=FALSE}
qplot(x = host_has_profile_pic, data = df_x) 
qplot(x = host_identity_verified, data = df_x)
qplot(x = host_is_superhost, data = df_x) + coord_flip()
qplot(x = instant_bookable, data = df_x)
qplot(x = is_business_travel_ready, data = df_x) 
qplot(x = is_location_exact, data = df_x)
qplot(x = require_guest_phone_verification, data = df_x)
qplot(x = require_guest_profile_picture, data = df_x)
qplot(x = requires_license, data = df_x)
```

These columns seem to comprise mostly of 'f's and 't's.

We need to figure out how to deal with this specific column since more than 45% of the values are missing. We'll get to that but first, let's take care of the other columns. 

```{r}
# View(table(tdf$host_has_profile_pic))
# View(table(tdf$host_identity_verified))
# View(table(tdf$host_is_superhost))
# View(table(tdf$instant_bookable))
# View(table(tdf$is_business_travel_ready))
# View(table(tdf$is_location_exact))
# View(table(tdf$require_guest_phone_verification))
# View(table(tdf$require_guest_profile_picture))
# View(table(tdf$requires_license))
```

Let's fix the discrepancies in the test data

```{r}
superhost_discrepancies <- c("Bed,Bath&Bike in Sunny Santa Monica", "Pristine Mid-Century Modern w 180° Canyon View!")

misplacedy <- c(775, 10274)

misplaced_tdf <- tdf[tdf$host_is_superhost %in% superhost_discrepancies, ]

tdf[tdf$host_is_superhost %in% superhost_discrepancies, 3:70] <- NA

tdf[tdf$X %in% misplacedy, ]
```

Convert t's and f's to 1s and 0s

```{r}
# 1. df$host_has_profile_pic - factor
df_x$host_has_profile_pic <- ifelse(df_x_main$host_has_profile_pic == "t", 1, 0)
qplot(x = host_has_profile_pic, data = df_x)
  # test data
tdf$host_has_profile_pic <- ifelse(tdf_x_main$host_has_profile_pic == "t", 1, 0)

# 2. df$host_identity_verified - factor
df_x$host_identity_verified <- ifelse(df_x_main$host_identity_verified == "t", 1, 0)
qplot(x = host_identity_verified, data = df_x)
  # test data
tdf$host_identity_verified <- ifelse(tdf_x_main$host_identity_verified == "t", 1, 0)

# 3. df$host_is_superhost - factor
df_x$host_is_superhost <- ifelse(df_x_main$host_is_superhost== "t", 1, 0)
qplot(x = host_is_superhost, data = df_x)
  # test data
tdf$host_is_superhost <- ifelse(tdf_x_main$host_is_superhost== "t", 1, 0)

# 4. df$instant_bookable - factor
df_x$instant_bookable <- ifelse(df_x_main$instant_bookable == "t", 1, 0)
qplot(x = instant_bookable, data = df_x)
  # test data
tdf$instant_bookable <- ifelse(tdf_x_main$instant_bookable == "t", 1, 0)  

# 5. df$is_business_travel_ready - factor
df_x$is_business_travel_ready <- ifelse(is.na(df_x_main$is_business_travel_ready), df_x_main$is_business_travel_ready, ifelse(df_x_main$is_business_travel_ready == "t", 1, 0))
qplot(x = is_business_travel_ready, data = df_x)
  # test data
tdf$is_business_travel_ready <- ifelse(is.na(tdf_x_main$is_business_travel_ready), tdf_x_main$is_business_travel_ready, ifelse(tdf_x_main$is_business_travel_ready == "t", 1, 0))

# 6. df$is_location_exact - factor
df_x$is_location_exact <- ifelse(df_x_main$is_location_exact == "t", 1, 0)
qplot(x = is_location_exact, data = df_x)
  # test data
tdf$is_location_exact <- ifelse(tdf_x_main$is_location_exact == "t", 1, 0)

# 7. df$require_guest_phone_verification - factor
df_x$require_guest_phone_verification <- ifelse(df_x_main$require_guest_phone_verification == "t", 1, 0)
qplot(x = require_guest_phone_verification, data = df_x)
  # test data
tdf$require_guest_phone_verification <- ifelse(tdf_x_main$require_guest_phone_verification == "t", 1, 0)

# 8. df$require_guest_profile_picture - factor
df_x$require_guest_profile_picture <- ifelse(df_x_main$require_guest_profile_picture == "t", 1, 0)
qplot(x = require_guest_profile_picture, data = df_x)
  # test data
tdf$require_guest_profile_picture <- ifelse(tdf_x_main$require_guest_profile_picture == "t", 1, 0)

# 9. df$requires_license - factor
df_x$requires_license <- ifelse(df_x_main$requires_license == "t", 1, 0)
qplot(x = requires_license, data = df_x)
  # test data
tdf$requires_license <- ifelse(tdf_x_main$requires_license == "t", 1, 0)

```

Moving on to other categorical variables -

1	bed_type	Factor
2	cancellation_policy	Factor
3	city	Factor
4	city_name	Factor
5	country	Factor
6	country_code	Factor
7	experiences_offered	Factor
# 8	host_has_profile_pic	Factor
# 9	host_identity_verified	Factor
# 10	host_is_superhost	Factor
11	host_location	Factor
12	host_neighbourhood	Factor
13	host_response_time	Factor
# 14	instant_bookable	Factor
# 15	is_business_travel_ready	Factor
# 16	is_location_exact	Factor
17	jurisdiction_names	Factor
18	license	Factor
19	market	Factor
20	neighbourhood	Factor
21	property_type	Factor
# 22	require_guest_phone_verification	Factor
# 23	require_guest_profile_picture	Factor
# 24	requires_license	Factor
25	room_type	Factor
26	smart_location	Factor
27	state	Factor

```{r, fig.height=15, fig.width=10}
qplot(df_x$bed_type) + coord_flip()
qplot(df_x$cancellation_policy) + coord_flip()
qplot(df_x$city) + coord_flip() # unclear - need to look at the table
qplot(df_x$city_name) + coord_flip()
qplot(df_x$country)+ coord_flip()
qplot(df_x$country_code)+ coord_flip()
qplot(df_x$experiences_offered)+ coord_flip()
qplot(df_x$host_location)+ coord_flip() # Unclear - need to look at the table
qplot(df_x$host_neighbourhood)+ coord_flip() # Unclear - need to look at the table
qplot(df_x$host_response_time)+ coord_flip()
qplot(df_x$jurisdiction_names)+ coord_flip() # Categorical list
qplot(df_x$license)+ coord_flip() # Unclear - need to look at the table
qplot(df_x$market)+ coord_flip() # Looks clean for the most part
qplot(df_x$neighbourhood)+ coord_flip() # Unclear - need to look at the table
qplot(df_x$property_type)+ coord_flip() # Looks neat for the most part
qplot(df_x$room_type)+ coord_flip() # clean
qplot(df_x$smart_location)+ coord_flip() # Unclear - need to look at the table
qplot(df_x$state)+ coord_flip() # needs to be cleaned
```

Table views for the variables with unclear plots -

```{r}
# View(table(df_x$city)) # 738 categories
# View(table(df_x$host_location)) # 2154 categories; Format like so - Liverpool, England, United Kingdom
# View(table(df_x$host_neighbourhood)) # 1303 categories
# View(table(df_x$license)) # Looks like some unique ID - 7474 many categories
# View(table(df_x$neighbourhood)) # 1093 categories; Examples - Woodside, Windsor
# View(table(df_x$smart_location)) # 750 categories - Can be cleaned by converting all to upper case
```

First, let's clean the state column -

```{r}
library(rapportools) # for trim.space

# View with all values in upper case

View(table(str_to_upper(df_x$state)))

# The data discrepancies are -

# 1. BAJA CALIFORNIA
# 2. NEW YORK
# 3. SECC TERRAZAS
# 4. MP

# Let's change that 

df_x$state <- trim.space(str_to_upper(df_x$state))

df_x$state[df_x$state == 'NEW YORK'] <- 'NY'
df_x$state[df_x$state == 'BAJA CALIFORNIA'] <- 'CA'
df_x$state[df_x$state == 'SECC TERRAZAS'] <- 'CA'
df_x$state[df_x$state == 'MP'] <- 'NY'

# There are only 17 samples for MD which can be changed to DC
# There are only 2 samples for NJ which can be changed to NY

df_x$state[df_x$state == 'MD'] <- 'DC'
df_x$state[df_x$state == 'NJ'] <- 'NY'

# There is a separate column for LA which can be changed to CA

df_x$state[df_x$state == 'LA'] <- 'CA'
unique(df_x$state)
  # test data

tdf$state <- trim.space(str_to_upper(tdf$state))
View(table(tdf$state))

tdf$state[tdf$state == 'LA'] <- 'CA'
tdf$state[tdf$state == 'MD'] <- 'DC'

unique(tdf$state)
```

```{r}
# View(sort(table(tdf$city), decreasing = T)) 
# View(table(tdf$host_location)) 
# View(table(tdf$host_neighbourhood)) 
# View(table(tdf$license)) 
# View(table(tdf$neighbourhood)) 
# View(table(tdf$smart_location)) 
```

They are pretty much okay.

Let's capitalize and trim these categorical columns -

```{r}

# city
df_x$city <- trim.space(str_to_upper(df_x$city))
  # test data
tdf$city <- trim.space(str_to_upper(tdf$city))

# city_name
df_x$city_name <- trim.space(str_to_upper(df_x$city_name))
  # test data
tdf$city_name <- trim.space(str_to_upper(tdf$city_name))

# host_location
df_x$host_location <- trim.space(str_to_upper(df_x$host_location))
  # test data
tdf$host_location <- trim.space(str_to_upper(tdf$host_location))

# host_neighborhood
df_x$host_neighbourhood <- trim.space(str_to_upper(df_x$host_neighbourhood))
  # test data
tdf$host_neighbourhood <- trim.space(str_to_upper(tdf$host_neighbourhood))

# neighborhood
df_x$neighbourhood <- trim.space(str_to_upper(df_x$neighbourhood))
  # test data
tdf$neighbourhood <- trim.space(str_to_upper(tdf$neighbourhood))

# smart_location
df_x$smart_location <- trim.space(str_to_upper(df_x$smart_location))
  # test data
tdf$smart_location <- trim.space(str_to_upper(tdf$smart_location)) 

```

Now let's view the number of categories for each of these variables and see if they have reduced -

```{r}
length(unique(df_x_main$city)) # 739
length(unique(df_x$city)) # 526
length(unique(df_x_main$host_location)) # 2155
length(unique(df_x$host_location)) # 2118
length(unique(df_x_main$host_neighbourhood)) # 1304
length(unique(df_x$host_neighbourhood)) # 1295
length(unique(df_x_main$neighborhood)) # 62392
length(unique(df_x$neighborhood)) # 62392
length(unique(df_x_main$smart_location)) # 751
length(unique(df_x$smart_location)) # 634
```

The test data -

```{r}
length(unique(tdf_x_main$city)) # 265
length(unique(tdf$city)) # 221
length(unique(tdf_x_main$host_location)) # 600
length(unique(tdf$host_location)) # 593
length(unique(tdf_x_main$host_neighbourhood)) # 879
length(unique(tdf$host_neighbourhood)) # 877
length(unique(tdf_x_main$neighborhood)) # 8194
length(unique(tdf$neighborhood)) # 8194
length(unique(tdf_x_main$smart_location)) # 268
length(unique(tdf$smart_location)) # 250
```

Now, the date columns; Let's convert them to date type; And then extract the number of years of experience the listing's host has had as a host; We shall also find the number of years since becoming a host did it take for them to get their first review - 

```{r}
df_x <- df_x %>%
  mutate(first_review = ymd(first_review),
         host_since = ymd(host_since),
         host_age = 2020 - year(host_since),
         start_to_review_gap = year(first_review) - year(host_since))

  # test data
tdf <- tdf %>%
  mutate(first_review = ymd(first_review),
         host_since = ymd(host_since),
         host_age = 2020 - year(host_since),
         start_to_review_gap = year(first_review) - year(host_since))
```

View the distribution of the host_age and start_to_review_gap -

```{r}
qplot(df_x$host_since, df_x$first_review)
qplot(df_x$host_age)
qplot(df_x$start_to_review_gap)
```

Replace the NAs in start_to_review_gap and host_age with the respective means of the column

```{r}
library(tidyr)

sTor_gap <- mean(df_x$start_to_review_gap)
df_x$start_to_review_gap <- replace_na(df_x$start_to_review_gap, sTor_gap)
  # test data
tdf$start_to_review_gap <- replace_na(tdf$start_to_review_gap, sTor_gap)

host_age_mean <- mean(df_x$host_age)
df_x$host_age <- replace_na(df_x$host_age, host_age_mean)
  # test data
tdf$host_age <- replace_na(tdf$start_to_review_gap, host_age_mean)

```

There are some start_to_review_gaps which are lesser than zero (where the first_review date is earlier than the host_since date)

Let's clean it up

```{r}
df_x$start_to_review_gap[df_x$start_to_review_gap < 0] <- sTor_gap
  # test data
tdf$start_to_review_gap[tdf$start_to_review_gap < 0] <- sTor_gap
```

Let's bucket these variables based on the quantiles -

```{r}
# host_age / experience

df_x <- df_x %>% 
  mutate(host_age_q = ntile(host_age, 5))


# df_x %>% 
#   mutate(host_age_q = ntile(host_age, 5)) %>%
#   group_by(host_age_q, host_age) %>%
#   summarize(n = n()) %>%
#   group_by(host_age_q) %>%
#   summarize(total = sum(n),
#             min_age = min(host_age),
#             max_age = max(host_age))

# 1	20000	2	4	
# 2	20000	4	5	
# 3	20000	5	6	
# 4	20000	6	8	
# 5	20000	8	12	


df_x <- df_x %>%	
	mutate( 
  		host_lowExp = ifelse(host_age_q == 1, 1, 0),
  		host_lowMedExp = ifelse(host_age_q == 2, 1, 0),
  		host_medExp = ifelse(host_age_q == 3, 1, 0),
  		host_medHighExp = ifelse(host_age_q == 4, 1, 0),
  		host_highExp = ifelse(host_age_q == 5, 1, 0)
  		)

tdf <- tdf %>%
  mutate(
      host_lowExp = ifelse((host_age >= 2) & (host_age < 4), 1, 0),
  		host_lowMedExp = ifelse((host_age >= 4) & (host_age < 5), 1, 0),
  		host_medExp = ifelse((host_age >= 5) & (host_age < 6), 1, 0),
  		host_medHighExp = ifelse((host_age >= 6) & (host_age < 8), 1, 0),
  		host_highExp = ifelse((host_age >= 8) & (host_age < 12), 1, 0) 
  )
```

Now the start_to_review_gap - 

Let's first check the outliers to impute -
```{r}
sTorR_OutVals <- boxplot(df_x$start_to_review_gap)$out
sTorR_OutVals
sTorR_TestOutVals <- boxplot(tdf$start_to_review_gap)$out
sTorR_TestOutVals
```

Change the outliers - 

```{r}
df_x$start_to_review_gap[df_x$start_to_review_gap > 7] <- 6
tdf$start_to_review_gap[tdf$start_to_review_gap > 7] <- 6
```


```{r}
df_x <- df_x %>% 
  mutate(sTor_gap_q = ntile(start_to_review_gap, 3))


# df_x %>%
#   mutate(sTor_gap_q = ntile(start_to_review_gap, 3)) %>%
#   group_by(sTor_gap_q, start_to_review_gap) %>%
#   summarize(n = n()) %>%
#   group_by(sTor_gap_q) %>%
#   summarize(total = sum(n),
#             min_age = min(start_to_review_gap),
#             max_age = max(start_to_review_gap))

# 1	33334	0	1	
# 2	33333	1	2	
# 3	33333	2	7	

df_x <- df_x %>%
	mutate(
  		NoGap_sTor = ifelse(sTor_gap_q == 1, 1, 0),
  		Yr1Gap_sTor = ifelse(sTor_gap_q == 2, 1, 0),
  		HighGap_sTor = ifelse(sTor_gap_q == 3, 1, 0)
  		)

tdf <- tdf %>%
  mutate(
      NoGap_sTor = ifelse(start_to_review_gap == 0, 1, 0),
  		Yr1Gap_sTor = ifelse(start_to_review_gap == 1, 1, 0),
  		HighGap_sTor = ifelse(start_to_review_gap >= 2, 1, 0)
  )

```

Dummy variables for state -

```{r}
df_x <- df_x %>%
	mutate(
  		In_CA = ifelse(state == 'CA', 1, 0),
  		In_CO = ifelse(state == 'CO', 1, 0),
  		In_DC = ifelse(state == 'DC', 1, 0),
  		In_IL = ifelse(state == 'IL', 1, 0),
  		In_MA = ifelse(state == 'MA', 1, 0),
  		In_NC = ifelse(state == 'NC', 1, 0),
  		In_NY = ifelse(state == 'NY', 1, 0),
  		In_OR = ifelse(state == 'OR', 1, 0),
  		In_TN = ifelse(state == 'TN', 1, 0),
  		In_TX = ifelse(state == 'TX', 1, 0),
  		In_WA = ifelse(state == 'WA', 1, 0)
  		)
  # test data

tdf <- tdf %>%
	mutate(
  		In_CA = ifelse(state == 'CA', 1, 0),
  		In_CO = ifelse(state == 'CO', 1, 0),
  		In_DC = ifelse(state == 'DC', 1, 0),
  		In_IL = ifelse(state == 'IL', 1, 0),
  		In_MA = ifelse(state == 'MA', 1, 0),
  		In_NC = ifelse(state == 'NC', 1, 0),
  		In_NY = ifelse(state == 'NY', 1, 0),
  		In_OR = ifelse(state == 'OR', 1, 0),
  		In_TN = ifelse(state == 'TN', 1, 0),
  		In_TX = ifelse(state == 'TX', 1, 0),
  		In_WA = ifelse(state == 'WA', 1, 0)
  		)

```

Let's also include city_name dummies. There might be more variance with these because parameters might change based on cities rather than state on the whole - 

```{r}
unique(df_x$city_name)
unique(tdf$city_name)
```

Let's create dummies then,

```{r}

df_x <- df_x %>%
	mutate(
  		In_NAS = ifelse(city_name == 'NASHVILLE', 1, 0),
  		In_LA = ifelse(city_name == 'LOS ANGELES', 1, 0),
  		In_SD = ifelse(city_name == 'SAN DIEGO', 1, 0),
  		In_WDC = ifelse(city_name == 'WASHINGTON DC', 1, 0),
  		In_NWO = ifelse(city_name == 'NEW ORLEANS', 1, 0),
  		In_SFO = ifelse(city_name == 'SAN FRANCISCO', 1, 0),
  		In_NYC = ifelse(city_name == 'NEW YORK', 1, 0),
  		In_SEA = ifelse(city_name == 'SEATTLE', 1, 0),
  		In_CHI = ifelse(city_name == 'CHICAGO', 1, 0),
  		In_BOS = ifelse(city_name == 'BOSTON', 1, 0),
  		In_AUS = ifelse(city_name == 'AUSTIN', 1, 0),
  		In_PO = ifelse(city_name == 'PORTLAND', 1, 0),
  		In_DEN = ifelse(city_name == 'DENVER', 1, 0),
  		In_SCU = ifelse(city_name == 'SANTA CRUZ', 1, 0),
  		In_OAK = ifelse(city_name == 'OAKLAND', 1, 0),
  		In_ASH = ifelse(city_name == 'ASHEVILLE', 1, 0)
  		)
  # test data

tdf <- tdf %>%
	mutate(
  		In_NAS = ifelse(city_name == 'NASHVILLE', 1, 0),
  		In_LA = ifelse(city_name == 'LOS ANGELES', 1, 0),
  		In_SD = ifelse(city_name == 'SAN DIEGO', 1, 0),
  		In_WDC = ifelse(city_name == 'WASHINGTON DC', 1, 0),
  		In_NWO = ifelse(city_name == 'NEW ORLEANS', 1, 0),
  		In_SFO = ifelse(city_name == 'SAN FRANCISCO', 1, 0),
  		In_NYC = ifelse(city_name == 'NEW YORK', 1, 0),
  		In_SEA = ifelse(city_name == 'SEATTLE', 1, 0),
  		In_CHI = ifelse(city_name == 'CHICAGO', 1, 0),
  		In_BOS = ifelse(city_name == 'BOSTON', 1, 0),
  		In_AUS = ifelse(city_name == 'AUSTIN', 1, 0),
  		In_PO = ifelse(city_name == 'PORTLAND', 1, 0),
  		In_DEN = ifelse(city_name == 'DENVER', 1, 0),
  		In_SCU = ifelse(city_name == 'SANTA CRUZ', 1, 0),
  		In_OAK = ifelse(city_name == 'OAKLAND', 1, 0),
  		In_ASH = ifelse(city_name == 'ASHEVILLE', 1, 0)
  		)

```

Cancellation Policy -

```{r}
# View(table(df_x$cancellation_policy))

# 7	strict	47372
# 5	moderate	30411
# 4	flexible	21837
# 8	super_strict_30	261
# 9	super_strict_60	106
# 6	no_refunds	4

strict <- c("no_refunds", "super_strict_60", "super_strict_30", "strict")


df_x <- df_x %>%
	mutate(
  		CancelPol_Strict = ifelse(cancellation_policy %in% strict, 1, 0),
  		CancelPol_Mod = ifelse(cancellation_policy == 'moderate', 1, 0),
  		CancelPol_Flexy = ifelse(cancellation_policy == 'flexible', 1, 0)
  		)
  # test data
tdf <- tdf %>%
	mutate(
  		CancelPol_Strict = ifelse(cancellation_policy %in% strict, 1, 0),
  		CancelPol_Mod = ifelse(cancellation_policy == 'moderate', 1, 0),
  		CancelPol_Flexy = ifelse(cancellation_policy == 'flexible', 1, 0)
  		)

```

Room Type and Property Type -

```{r}
# View(table(df_x$room_type))

# 1	Entire home/apt	60892
# 2	Private room	36617
# 3	Shared room	2472

# View(table(tdf$room_type))

# 1	Entire home/apt	7425
# 2	Private room	4480
# 3	Shared room	300

df_x <- df_x %>%
	mutate(
  		WholePlace = ifelse(room_type == 'Entire home/apt', 1, 0),
  		PrivateRoom = ifelse(room_type == 'Private room', 1, 0),
  		SharedRoom = ifelse(room_type == 'Shared room', 1, 0)
  		)
  # test data
tdf <- tdf %>%
	mutate(
  		WholePlace = ifelse(room_type == 'Entire home/apt', 1, 0),
  		PrivateRoom = ifelse(room_type == 'Private room', 1, 0),
  		SharedRoom = ifelse(room_type == 'Shared room', 1, 0)
  		)

```


Property type - 

```{r}
df_x$property_type <- trim.space(str_to_upper(df_x$property_type))
tdf$property_type <- trim.space(str_to_upper(tdf$property_type))

# View(table(df_x$property_type))

apartment_types = c("APARTMENT", "CONDOMINIUM", "LOFT", "IN-LAW")
house_types = c("HOUSE", "TOWNHOUSE", "GUESTHOUSE", "TINY HOUSE", "BUNGALOW", "VILLA", "CASA PARTICULAR (CUBA)")
hotel_types = c("BED & BREAKFAST", "BED AND BREAKFAST", "SERVICED APARTMENT", "HOTEL", "APARTHOTEL", "GUEST SUITE")
holiday_types = c("RESORT", "VACATION HOME", "CABIN", "CHALET", "TIMESHARE", "BOAT", "TREEHOUSE", "YURT", "COTTAGE", "HUT", "ISLAND", "BOUTIQUE HOTEL", "CASTLE", "EARTH HOUSE", "CAVE", "TRAIN", "FARM STAY", "BARN", "LIGHTHOUSE", "NATURE LODGE", "PLANE")
other_types = c("OTHER", "DORM", "CAMPER/RV", "HOSTEL", "TENT", "TIPI")

df_x <- df_x %>%
	mutate(
  		propertyApartment = ifelse(property_type %in% apartment_types, 1, 0),
  		propertyHouse = ifelse(property_type %in% house_types, 1, 0),
  		propertyHotel = ifelse(property_type %in% hotel_types, 1, 0),
  		propertyHoliday = ifelse(property_type %in% holiday_types, 1, 0),
  		propertyOther = ifelse(property_type %in% other_types, 1, 0)
  		)
  # test data
# View(table(tdf$property_type))

tdf <- tdf %>%
	mutate(
  		propertyApartment = ifelse(property_type %in% apartment_types, 1, 0),
  		propertyHouse = ifelse(property_type %in% house_types, 1, 0),
  		propertyHotel = ifelse(property_type %in% hotel_types, 1, 0),
  		propertyHoliday = ifelse(property_type %in% holiday_types, 1, 0),
  		propertyOther = ifelse(property_type %in% other_types, 1, 0)
  		)
```

Bed Type -

```{r}
# View(table(df_x$bed_type))
# View(table(tdf$bed_type))
# View(table(df_x$bed_type, df_y$high_booking_rate))
  
# 3	  Airbed	0	449
# 4	  Couch	0	213
# 5	  Futon	0	805
# 6	  Pull-out Sofa	0	556
# 7	  Real Bed	0	72828
# 
# 10	Airbed	1	89
# 11	Couch	1	48
# 12	Futon	1	191
# 13	Pull-out Sofa	1	164
# 14	Real Bed	1	24638

uncomfyBeds = c("Airbed", "Couch", "Futon", "Pull-out Sofa")

df_x <- df_x %>%
	mutate(
  		bed_Real = ifelse(bed_type == 'Real Bed', 1, 0),
  		bed_Uncomfy = ifelse(bed_type %in% uncomfyBeds, 1, 0)
  		)
  # test data
tdf <- tdf %>%
	mutate(
  		bed_Real = ifelse(bed_type == 'Real Bed', 1, 0),
  		bed_Uncomfy = ifelse(bed_type %in% uncomfyBeds, 1, 0)
  		)
```

host_response_time

```{r}
# View(table(df_x$host_response_time, df_y$high_booking_rate))
# View(table(df_x$host_response_time))
# View(table(tdf$host_response_time))

# 1	a few days or more	0	1350
# 2	f	0	0
# 3	within a day	0	9800
# 4	within a few hours	0	14333
# 5	within an hour	0	33865
# 6	a few days or more	1	55
# 7	f	1	0
# 8	within a day	1	857
# 9	within a few hours	1	2929
# 10	within an hour	1	21008

# replacing na with the second most popular category
df_x$host_response_time <- replace_na(df_x$host_response_time, 'within a few hours')

df_x <- df_x %>%
	mutate(
  		hRes_FewDays = ifelse(host_response_time == 'a few days or more', 1, 0),
  		hRes_1Day = ifelse(host_response_time == 'within a day', 1, 0),
  		hRes_FewHours = ifelse(host_response_time == 'within a few hours', 1, 0),
  		hRes_1Hour = ifelse(host_response_time == 'within an hour', 1, 0)
  		)
  # test data
tdf <- tdf %>%
	mutate(
  		hRes_FewDays = ifelse(host_response_time == 'a few days or more', 1, 0),
  		hRes_1Day = ifelse(host_response_time == 'within a day', 1, 0),
  		hRes_FewHours = ifelse(host_response_time == 'within a few hours', 1, 0),
  		hRes_1Hour = ifelse(host_response_time == 'within an hour', 1, 0)
  		)

```


```{r}
View(df_x$host_verifications)
View(df_x$amenities)
```



Some text mining on the columns with categorical lists -

```{r}
library(qdap)

df_x$host_verifications <- as.character(df_x$host_verifications)
df_x$host_verifications <- trim.space(str_to_lower(df_x$host_verifications))
freq_verifs <- freq_terms(df_x$host_verifications, 50)

```

```{r}
plot(freq_verifs)
```

Dummies for number of host verifications

```{r}

df_x <- df_x %>%
	mutate(
  		No_of_Verifs = str_count(df_x$host_verifications, ",") + 1
  		)

# View(table(df_x$No_of_Verifs))

# 1	  1	  241
# 2	  2	  1978
# 3	  3	  16077
# 4	  4	  35876
# 5	  5	  23967
# 6	  6	  10773
# 7	  7	  4552
# 8	  8	  3522
# 9	  9	  1984
# 10	10	707
# 11	11	217
# 12	12	71
# 13	13	14
# 14	14	2

df_x <- df_x %>%
	mutate(
  		verifs_vLow = ifelse((No_of_Verifs >= 1) & (No_of_Verifs <= 2), 1, 0),
  		verifs_Med = ifelse((No_of_Verifs >= 3) & (No_of_Verifs <= 5), 1, 0),
  		verifs_High = ifelse((No_of_Verifs >= 6) & (No_of_Verifs <= 8), 1, 0),
  		verifs_VHigh = ifelse(No_of_Verifs >= 9, 1, 0)
  		)
  # test data
tdf <- tdf %>%
	mutate(
  		No_of_Verifs = str_count(tdf$host_verifications, ",") + 1
  		)

tdf <- tdf %>%
	mutate(
  		verifs_vLow = ifelse((No_of_Verifs >= 1) & (No_of_Verifs <= 2), 1, 0),
  		verifs_Med = ifelse((No_of_Verifs >= 3) & (No_of_Verifs <= 5), 1, 0),
  		verifs_High = ifelse((No_of_Verifs >= 6) & (No_of_Verifs <= 8), 1, 0),
  		verifs_VHigh = ifelse(No_of_Verifs >= 9, 1, 0)
  		)

```

Create further dummies based on popular verification types -

```{r}

# 1 phone 2 reviews 3 email 4 jumio 5 kba 6 facebook 7 governmentid 8 workemail 9 offlinegovernmentid 10 google

df_x <- df_x %>%
  mutate(
    facebookVer = ifelse(grepl("facebook", host_verifications), 1, 0),
    googleVer = ifelse(grepl("google", host_verifications), 1, 0),
    govtIDVer = ifelse(grepl("government_id", host_verifications), 1, 0),
    jumioVer = ifelse(grepl("jumio", host_verifications), 1, 0),
    kbaVer = ifelse(grepl("kba", host_verifications), 1, 0)
  )
  # test data

tdf <- tdf %>%
  mutate(
    facebookVer = ifelse(grepl("facebook", host_verifications), 1, 0),
    googleVer = ifelse(grepl("google", host_verifications), 1, 0),
    govtIDVer = ifelse(grepl("government_id", host_verifications), 1, 0),
    jumioVer = ifelse(grepl("jumio", host_verifications), 1, 0),
    kbaVer = ifelse(grepl("kba", host_verifications), 1, 0)
  )

```

Now, the harder one - amenities -

```{r}
df_x$amenities <- as.character(df_x$amenities)
df_x$amenities <- trim.space(str_to_lower(df_x$amenities))
df_x$amenities <- str_replace_all(df_x$amenities, " ", "_")
# View(df_x$amenities)
  # test data
tdf$amenities <- as.character(tdf$amenities)
tdf$amenities <- trim.space(str_to_lower(tdf$amenities))
tdf$amenities <- str_replace_all(tdf$amenities, " ", "_")
```

Further, let's count the number of amenities as well as the most popular amenities -

```{r}
df_x <- df_x %>%
  mutate(No_of_Amens = str_count(amenities, ",") + 1)

# df_x %>% 
#   mutate(amens_q = ntile(No_of_Amens, 5)) %>%
#   group_by(amens_q, No_of_Amens) %>%
#   summarize(n = n()) %>%
#   group_by(amens_q) %>%
#   summarize(total = sum(n),
#             min_age = min(No_of_Amens),
#             max_age = max(No_of_Amens))

# 1	19999	1	  13	
# 2	19998	13	17	
# 3	19998	17	21	
# 4	19998	21	25	
# 5	19998	25	78

amens_avg <- mean(df_x$No_of_Amens)

df_x$No_of_Amens <- replace_na(df_x$No_of_Amens, amens_avg)

df_x <- df_x %>%
  mutate(
    vlowAmens = ifelse((No_of_Amens >= 1) & (No_of_Amens < 13), 1, 0),
    lowAmens = ifelse((No_of_Amens >= 13) & (No_of_Amens < 17), 1, 0),
    medAmens = ifelse((No_of_Amens >= 17) & (No_of_Amens < 21), 1, 0),
    highAmens = ifelse((No_of_Amens >= 21) & (No_of_Amens < 25), 1, 0),
    vhighAmens = ifelse(No_of_Amens > 25, 1, 0)
         )
  # test data
tdf <- tdf %>%
  mutate(No_of_Amens = str_count(amenities, ",") + 1)

tdf <- tdf %>%
  mutate(
    vlowAmens = ifelse((No_of_Amens >= 1) & (No_of_Amens < 13), 1, 0),
    lowAmens = ifelse((No_of_Amens >= 13) & (No_of_Amens < 17), 1, 0),
    medAmens = ifelse((No_of_Amens >= 17) & (No_of_Amens < 21), 1, 0),
    highAmens = ifelse((No_of_Amens >= 21) & (No_of_Amens < 25), 1, 0),
    vhighAmens = ifelse(No_of_Amens > 25, 1, 0)
         )

```

```{r, fig.height=10, fig.width=10}
k <- gsub(",", " ", df_x$amenities)
freq_amenities <- freq_terms(k, 50)
plot(freq_amenities)
```

More dummies for specific amenities -

```{r}

kitchen_amens <- "kitchen|microwave|stove"
kitchen2_amens <- "coffee_maker|refrigerator"
heat_amens <- "heating"
ac_amens <- "air_conditioning"
tv_amens <- "tv|cable_tv"
wifi_amens <- "internet|wireless_internet|wifi"
pets_amens <- "pets_allowed|dogs"
luxury_amens <- "gym|hot_tub|pool|indoor_fireplace|breakfast"
petsLiveHere <- "pets_live_on_this_property"
workspace_amens <- "laptop_friendly_workspace"
parking_amens <- "free_parking_on_premises"
extrabedding <- "bed_linens|extra_pillows_and_blankets"
elevator_amens <- "elevator|elevator_in_building"
privacy_amens <- "private_entrance|lock_on_bedroom_door"

df_x[grep(kitchen_amens, df_x$amenities, value = F), "hasKitchen1"] <- 1
df_x[grep(kitchen2_amens, df_x$amenities, value = F), "hasKitchen2"] <- 1
df_x[grep(heat_amens, df_x$amenities, value = F), "hasHeating"] <- 1
df_x[grep(ac_amens, df_x$amenities, value = F), "hasAC"] <- 1
df_x[grep(tv_amens, df_x$amenities, value = F), "hasTV"] <- 1
df_x[grep(wifi_amens, df_x$amenities, value = F), "hasWiFi"] <- 1
df_x[grep(pets_amens, df_x$amenities, value = F), "PetsAllowed"] <- 1
df_x[grep(luxury_amens, df_x$amenities, value = F), "hasLuxuryAmens"] <- 1
df_x[grep(petsLiveHere, df_x$amenities, value = F), "petsLiveHere"] <- 1
df_x[grep(workspace_amens, df_x$amenities, value = F), "hasWorkspace"] <- 1
df_x[grep(parking_amens, df_x$amenities, value = F), "hasFreeParking"] <- 1
df_x[grep(extrabedding, df_x$amenities, value = F), "extraBedding"] <- 1
df_x[grep(elevator_amens, df_x$amenities, value = F), "hasElevator"] <- 1
df_x[grep(privacy_amens, df_x$amenities, value = F), "hasPrivacyAmens"] <- 1
  # test data
tdf[grep(kitchen_amens, tdf$amenities, value = F), "hasKitchen1"] <- 1
tdf[grep(kitchen2_amens, tdf$amenities, value = F), "hasKitchen2"] <- 1
tdf[grep(heat_amens, tdf$amenities, value = F), "hasHeating"] <- 1
tdf[grep(ac_amens, tdf$amenities, value = F), "hasAC"] <- 1
tdf[grep(tv_amens, tdf$amenities, value = F), "hasTV"] <- 1
tdf[grep(wifi_amens, tdf$amenities, value = F), "hasWiFi"] <- 1
tdf[grep(pets_amens, tdf$amenities, value = F), "PetsAllowed"] <- 1
tdf[grep(luxury_amens, tdf$amenities, value = F), "hasLuxuryAmens"] <- 1
tdf[grep(petsLiveHere, tdf$amenities, value = F), "petsLiveHere"] <- 1
tdf[grep(workspace_amens, tdf$amenities, value = F), "hasWorkspace"] <- 1
tdf[grep(parking_amens, tdf$amenities, value = F), "hasFreeParking"] <- 1
tdf[grep(extrabedding, tdf$amenities, value = F), "extraBedding"] <- 1
tdf[grep(elevator_amens, tdf$amenities, value = F), "hasElevator"] <- 1
tdf[grep(privacy_amens, tdf$amenities, value = F), "hasPrivacyAmens"] <- 1


```

Replace NAs in the newly created columns with 0s

```{r}
amenCols <- c("hasKitchen1", "hasKitchen2", "hasHeating", "hasAC", 
              "hasTV", "hasWiFi", "PetsAllowed", "hasLuxuryAmens", 
              "petsLiveHere", "hasWorkspace", "hasFreeParking", 
              "extraBedding", "hasElevator", "hasPrivacyAmens")

df_x$hasKitchen1 <- replace_na(df_x$hasKitchen1, 0)
df_x$hasKitchen2 <- replace_na(df_x$hasKitchen2, 0)
df_x$hasHeating <- replace_na(df_x$hasHeating, 0)
df_x$hasAC <- replace_na(df_x$hasAC, 0)
df_x$hasTV <- replace_na(df_x$hasTV, 0)
df_x$hasWiFi <- replace_na(df_x$hasWiFi, 0)
df_x$PetsAllowed <- replace_na(df_x$PetsAllowed, 0)
df_x$hasLuxuryAmens <- replace_na(df_x$hasLuxuryAmens, 0)
df_x$petsLiveHere <- replace_na(df_x$petsLiveHere, 0)
df_x$hasWorkspace <- replace_na(df_x$hasWorkspace, 0)
df_x$hasFreeParking <- replace_na(df_x$hasFreeParking, 0)
df_x$extraBedding <- replace_na(df_x$extraBedding, 0)
df_x$hasElevator <- replace_na(df_x$hasElevator, 0)
df_x$hasPrivacyAmens <- replace_na(df_x$hasPrivacyAmens, 0)
  # test data
tdf$hasKitchen1 <- replace_na(tdf$hasKitchen1, 0)
tdf$hasKitchen2 <- replace_na(tdf$hasKitchen2, 0)
tdf$hasHeating <- replace_na(tdf$hasHeating, 0)
tdf$hasAC <- replace_na(tdf$hasAC, 0)
tdf$hasTV <- replace_na(tdf$hasTV, 0)
tdf$hasWiFi <- replace_na(tdf$hasWiFi, 0)
tdf$PetsAllowed <- replace_na(tdf$PetsAllowed, 0)
tdf$hasLuxuryAmens <- replace_na(tdf$hasLuxuryAmens, 0)
tdf$petsLiveHere <- replace_na(tdf$petsLiveHere, 0)
tdf$hasWorkspace <- replace_na(tdf$hasWorkspace, 0)
tdf$hasFreeParking <- replace_na(tdf$hasFreeParking, 0)
tdf$extraBedding <- replace_na(tdf$extraBedding, 0)
tdf$hasElevator <- replace_na(tdf$hasElevator, 0)
tdf$hasPrivacyAmens <- replace_na(tdf$hasPrivacyAmens, 0)

```

I'd like to see if smoking is allowed or not from the house rules column -

For that, trim spaces and convert to lowercase first -

```{r}

df_x$house_rules <- as.character(df_x$house_rules)
df_x$house_rules <- trim.space(str_to_lower(df_x$house_rules))
  # test data
tdf$house_rules <- as.character(tdf$house_rules)
tdf$house_rules <- trim.space(str_to_lower(tdf$house_rules))

```


```{r}
df_x[grep("no smoking", df_x$house_rules, value = F), "NoSmoking"] <- 1
df_x$NoSmoking[is.na(df_x$NoSmoking)] <- 0
  # test data
tdf[grep("no smoking", tdf$house_rules, value = F), "NoSmoking"] <- 1
tdf$NoSmoking[is.na(tdf$NoSmoking)] <- 0

```

Is host from USA?

```{r}
df_x$host_location <- trim.space(str_to_lower(df_x$host_location))
  # test data
tdf$host_location <- trim.space(str_to_lower(tdf$host_location))

df_x <- df_x %>%
  mutate(
    isHost_in_US = ifelse(grepl("united states", host_location), 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    isHost_in_US = ifelse(grepl("united states", host_location), 1, 0)
  )

```

More processing on the numerical columns now -

accommodates
availability_30
availability_365
availability_60
availability_90
bathrooms
bedrooms
beds
cleaning_fee
extra_people
guests_included

host_listings_count
host_response_rate
host_total_listings_count

maximum_nights
minimum_nights

price


```{r}

# View(table(df_x$guests_included)) There are some 0s
# View(table(df_x$accommodates)) There are no 0s

# Replacing the 0s and NAs in guests_included with 1s, the most popular category

df_x$guests_included[df_x$guests_included == 0] <- 1
df_x$guests_included <- replace_na(df_x$guests_included, 1)
 # test data
tdf$guests_included[tdf$guests_included == 0] <- 1
tdf$guests_included <- replace_na(tdf$guests_included, 1)

# The price can also include the cleaning fee

# summary(df_x$cleaning_fee) - median is 50

df_x$cleaning_fee <- replace_na(df_x$cleaning_fee, 50)
  # test data
tdf$cleaning_fee <- replace_na(tdf$cleaning_fee, 50)

# The security deposit has 40K NAs

# summary(df_x$security_deposit)

df_x$security_deposit <- replace_na(df_x$security_deposit, 200)
  # test data
tdf$security_deposit <- replace_na(tdf$security_deposit, 200)

df_x <- df_x %>%
  mutate(
    bathroomGuestRatio = bathrooms/accommodates,
    bedroomsGuestRatio = bedrooms/accommodates,
    bedsGuestsRatio = beds/accommodates,
    pricePerGuest = (price + cleaning_fee)/guests_included,
    sec_dep_perc = ifelse(price >=1 , (100*security_deposit)/price, 60)
  )
  # test data
tdf <- tdf %>%
  mutate(
    bathroomGuestRatio = bathrooms/accommodates,
    bedroomsGuestRatio = bedrooms/accommodates,
    bedsGuestsRatio = beds/accommodates,
    pricePerGuest = (price + cleaning_fee)/guests_included,
    sec_dep_perc = ifelse(price >=1 , (100*security_deposit)/price, 60)
  )
```

There are some sec_dep_perc that are greater than 100!

Let's change those -

```{r}
df_x$sec_dep_perc[df_x$sec_dep_perc > 100] <- 60
  # test data
tdf$sec_dep_perc[tdf$sec_dep_perc > 100] <- 60
```

Now, we can bin the security deposits -

```{r}
df_x <- df_x %>%
  mutate(
    secDep0 = ifelse(sec_dep_perc == 0, 1, 0),
    secDepGen = ifelse((sec_dep_perc > 0) & (sec_dep_perc <= 60), 1, 0),
    secDepHigh = ifelse(sec_dep_perc > 60, 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    secDep0 = ifelse(sec_dep_perc == 0, 1, 0),
    secDepGen = ifelse((sec_dep_perc > 0) & (sec_dep_perc <= 60), 1, 0),
    secDepHigh = ifelse(sec_dep_perc > 60, 1, 0)
  )
```

The pricePerGuest can be further divided into dummies based on quantiles -

```{r}
# df_x %>% 
#   mutate(pPG_q = ntile(pricePerGuest, 5)) %>%
#   group_by(pPG_q, pricePerGuest) %>%
#   summarize(n = n()) %>%
#   group_by(pPG_q) %>%
#   summarize(total = sum(n),
#             min_age = min(pricePerGuest),
#             max_age = max(pricePerGuest))
# 
# summary(df_x$pricePerGuest)

df_x <- df_x %>%
  mutate(
    vlow_pPG = ifelse((pricePerGuest >= 0) & (pricePerGuest < 44), 1, 0),
    low_pPG = ifelse((pricePerGuest >= 44) & (pricePerGuest < 87.5), 1, 0),
    med_pPG = ifelse((pricePerGuest >= 87.5) & (pricePerGuest < 250), 1, 0),
    high_pPG = ifelse((pricePerGuest >= 250) & (pricePerGuest < 1000), 1, 0),
    vHigh_pPG = ifelse(pricePerGuest >= 1000, 1, 0)
  )
  # test data
tdf <- tdf%>%
  mutate(
    vlow_pPG = ifelse((pricePerGuest >= 0) & (pricePerGuest < 44), 1, 0),
    low_pPG = ifelse((pricePerGuest >= 44) & (pricePerGuest < 87.5), 1, 0),
    med_pPG = ifelse((pricePerGuest >= 87.5) & (pricePerGuest < 250), 1, 0),
    high_pPG = ifelse((pricePerGuest >= 250) & (pricePerGuest < 1000), 1, 0),
    vHigh_pPG = ifelse(pricePerGuest >= 1000, 1, 0)
  )
```

Making dummies of bathroomGuestRatio, bedsGuestRatio, and bedroomsGuestRation -

First, bedsGuestsRatio -

```{r}

# df_x %>%
#   mutate(bGR_q = ntile(bedsGuestsRatio, 5)) %>%
#   group_by(bGR_q, bedsGuestsRatio) %>%
#   summarize(n = n()) %>%
#   group_by(bGR_q) %>%
#   summarize(total = sum(n),
#             min_age = min(bedsGuestsRatio),
#             max_age = max(bedsGuestsRatio))
# 
# summary(df_x$bedsGuestsRatio)

df_x$bedsGuestsRatio <- replace_na(df_x$bedsGuestsRatio, 1)
  # test data
tdf$bedsGuestsRatio <- replace_na(tdf$bedsGuestsRatio, 1)

df_x <- df_x %>%
  mutate(
    beds_Comfy = ifelse((bedsGuestsRatio >= 0.7333333) & (bedsGuestsRatio < 1.3), 1, 0),
    beds_Cramped = ifelse(bedsGuestsRatio < 0.7333333, 1, 0),
    beds_Excess = ifelse(bedsGuestsRatio > 1.3, 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    beds_Comfy = ifelse((bedsGuestsRatio >= 0.7333333) & (bedsGuestsRatio < 1.3), 1, 0),
    beds_Cramped = ifelse(bedsGuestsRatio < 0.7333333, 1, 0),
    beds_Excess = ifelse(bedsGuestsRatio > 1.3, 1, 0)
  )

```

Second, bathroomGuestRatio

```{r}
# df_x %>%
#   mutate(baGR_q = ntile(bathroomGuestRatio, 5)) %>%
#   group_by(baGR_q, bathroomGuestRatio) %>%
#   summarize(n = n()) %>%
#   group_by(baGR_q) %>%
#   summarize(total = sum(n),
#             min_age = min(bathroomGuestRatio),
#             max_age = max(bathroomGuestRatio))
# 
# summary(df_x$bathroomGuestRatio)

df_x$bathroomGuestRatio <- replace_na(df_x$bedsGuestsRatio, 0.7)
  # test data
tdf$bathroomGuestRatio <- replace_na(tdf$bathroomGuestRatio, 0.7)

df_x <- df_x %>%
  mutate(
    baths_Comfy = ifelse((bedsGuestsRatio >= 0.5) & (bedsGuestsRatio < 1.2), 1, 0),
    baths_Cramped = ifelse(bedsGuestsRatio < 0.5, 1, 0),
    baths_Excess = ifelse(bedsGuestsRatio > 1.2, 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    baths_Comfy = ifelse((bedsGuestsRatio >= 0.5) & (bedsGuestsRatio < 1.2), 1, 0),
    baths_Cramped = ifelse(bedsGuestsRatio < 0.5, 1, 0),
    baths_Excess = ifelse(bedsGuestsRatio > 1.2, 1, 0)
  )
```

Finally, bedroomsGuestRation 

```{r}
# summary(df_x$bedroomsGuestRatio)

df_x$bedroomsGuestRatio <- replace_na(df_x$bedroomsGuestRatio, 0.5)
  # test data
tdf$bedroomsGuestRatio <- replace_na(tdf$bedroomsGuestRatio, 0.5)

df_x <- df_x %>%
  mutate(
    bedrooms_Comfy = ifelse((bedroomsGuestRatio >= 0.5) & (bedroomsGuestRatio < 1.2), 1, 0),
    bedrooms_Cramped = ifelse(bedroomsGuestRatio < 0.5, 1, 0),
    bedrooms_Excess = ifelse(bedroomsGuestRatio > 1.2, 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    bedrooms_Comfy = ifelse((bedroomsGuestRatio >= 0.5) & (bedroomsGuestRatio < 1.2), 1, 0),
    bedrooms_Cramped = ifelse(bedroomsGuestRatio < 0.5, 1, 0),
    bedrooms_Excess = ifelse(bedroomsGuestRatio > 1.2, 1, 0)
  )
```

There are columns with text in them -
  
1. df$access - Something like 'I like to feel right at home'
2. df$amenities - {TV, \"Cable TV"}
3. df$description - "Vacation in this Nashville home featuring a premier location"
4. df$host_about - "I am from Virginia, USA and my wife is from Istanbul, Turkey"
5. df$host_location - "Nashville, Tennessee, United States", "Los Angeles, California, United States"
6. df$host_name - May & Eric, Jonathon, Jeremy, Gene, Holly, Nathan, Gregg, Alicia, Laura, Raymond
7. df$host_neighbourhood - , Silver Lake, East Village, Near Northeast/H Street Corridor, Bayou St. John
8. df$host_verifications - "['email', 'phone', 'google', 'reviews']", "['email', 'phone', 'reviews', 'jumio']"
9. df$house_rules - "No pets, parties, or indoor smoking. Feel free to use everything in kitchen bu"
10. df$interaction - "Don't hesitate to call or text any time throughout your stay! Where you are looking fo"
11. df$jurisdiction_names - "City of Los Angeles, CA", "SAN DIEGO, SAN DIEGO TOURISM MARKETING DISTRICT A, SAN"
12. df$license - "17STR-04969", "1075925", "17STR-14190"
13. df$name - "BRAND NEW ! NASHVILLE LOFT", "Silverlake Hills Home with View"
14. df$neighborhood_overview - "This modern loft is locate in a nice neighborhood near to the centennial park and just"
15. df$neighbourhood - "Silver Lake, Pacific Beach, Near Northeast/H Street Corridor, Bayou St. John, Lower H"
16. df$notes - "Its a fun beach town - the beach, the bay, the great restaurants, the wonderfu"
17. df$space - "Beautiful brand new loft in a central location. Near Vandy and Centennial park,only 2"
18. df$street - "Nashville, TN, United States", "Silver Lake, Los Angeles, CA 90026, United States"
19. df$summary - "Vacation in this Nashville home featuring a premier location - just 2 miles from downt"
20. df$transit - "Ubers are everywhere. We also have car2go's everywhere if you have an account"

----------------------------------------------------------------------------------------------------------------------------

Let's treat the numerical columns which we are not going to be binning -

Scale availabilities and accommodates -

```{r}

# summary(df_x$availability_30)
# summary(df_x$availability_60)
# summary(df_x$availability_90)
avail_vars <- df_x %>%
  select(availability_30, availability_60, availability_90, availability_365, accommodates)

processed_vars <- preProcess(avail_vars, method = c("YeoJohnson"))

df_x <- predict(processed_vars, df_x)
  # test data
tdf <- predict(preProcess(tdf %>% select(availability_30, availability_60, availability_90, availability_365, accommodates), method = c("YeoJohnson")), tdf)

```

Let's take a look at cleaning fee and replace NAs with the median

```{r}
qplot(df_x$cleaning_fee)
qplot(df_x$security_deposit)

df_x$cleaning_fee <- replace_na(df_x$cleaning_fee, 50)

summary(df_x$cleaning_fee)
```

Create standardized columns for price, cleaning_fee, security_deposit, maximum_nights

```{r}
processed_vars <- preProcess(df_x %>% select(price, extra_people, maximum_nights), method = "YeoJohnson")
df_x <- predict(processed_vars, df_x)
  # test data
tdf <- predict(preProcess(tdf %>% select(price, extra_people, maximum_nights), method = "YeoJohnson"), tdf)
```

Minimum Nights dummies

```{r}

# summary(df_x$minimum_nights)

# View(table(df_x$minimum_nights))

df_x$minimum_nights[df_x$minimum_nights > 1250] <- 100 # random
# summary(df_x$minimum_nights)

df_x <- df_x %>%
  mutate(
    minNigh1 = ifelse(minimum_nights == 1, 1, 0),
    minNigh2 = ifelse(minimum_nights == 2, 1, 0),
    minNigh3 = ifelse(minimum_nights == 3, 1, 0),
    minNight_Excess = ifelse(minimum_nights > 3, 1, 0)
  )
  # test data
tdf <- tdf %>%
  mutate(
    minNigh1 = ifelse(minimum_nights == 1, 1, 0),
    minNigh2 = ifelse(minimum_nights == 2, 1, 0),
    minNigh3 = ifelse(minimum_nights == 3, 1, 0),
    minNight_Excess = ifelse(minimum_nights > 3, 1, 0)
  )
```

Dummies for presence of cleaning fee and security deposit -

(Commented because combined cleaning_fee with price and created dummies for security_deposit)

```{r}
# df_x <- df_x %>%
#   mutate(
#     isCleaningFee = ifelse(is.na(cleaning_fee) | cleaning_fee == 0, 0, 1),
#     isSecurityDeposit = ifelse(is.na(security_deposit) | security_deposit == 0, 0, 1)
#   )
#   # test data
# tdf <- tdf %>%
#   mutate(
#     isCleaningFee = ifelse(is.na(cleaning_fee) | cleaning_fee == 0, 0, 1),
#     isSecurityDeposit = ifelse(is.na(security_deposit) | security_deposit == 0, 0, 1)
#   )
```

host_response_rate, host_listings_count, host_total_listings_count

```{r}
# qplot(df_x_main$host_listings_count, df_x_main$host_total_listings_count)

# Both are same

df_x$host_response_rate <- replace_na(df_x$host_response_rate, 100)
  # test data
tdf$host_response_rate <- replace_na(tdf$host_response_rate, 100)

# Scale

df_x <- predict(preProcess(df_x %>% select(host_listings_count, host_response_rate), method = c("YeoJohnson")), df_x)
  # test data
tdf <- predict(preProcess(tdf %>% select(host_listings_count, host_response_rate), method = c("YeoJohnson")), tdf)
```

